Automated Verification of Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2019-10-17 Tex/Old text/main.tex
thesis updated text
revised Chapter 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
Thesis update
updated thesis title
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\documentclass[12pt,twoside]{report}
%\documentclass[12pt,a4paper]{ltxdoc}
%\documentclass[12pt,a4paper]{article}
\usepackage{lmodern}			% Usa a fonte Latin Modern			
\usepackage[T1]{fontenc}		% seleção de códigos de fonte.
\usepackage[utf8]{inputenc}		% determina a codificação utilizada (conversão automática dos acentos)
\usepackage{hyperref}  			% controla a formação do índice
\usepackage{parskip}			% espaçamento entre os parágrafos
\usepackage{microtype} 			% para melhorias de justificação
\usepackage{morefloats}			% permite mais floats
\usepackage{setspace}
%\singlespacing
\onehalfspacing
%\doublespacing
%\setstretch{1.1}

%\documentclass[10pt,a4paper]{article}
%\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{algorithm,algorithmic}
\usepackage{xcolor}
%Alessandro input: makecell package to permite line break inside tables
\usepackage{makecell}
\usepackage[alf]{abntex2cite}	% citacoes

@@

\title{Automated Verification Applied to Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation}
\author{Alessandro Trindade}
\date{31 July 2019}

@@

\input{abstract}
\pagestyle{empty}
%\thispagestyle{empty}

@@

\chapter{Introduction}
\pagenumbering{arabic}
\pagestyle{fancy}
\fancyhead{}
\fancyhead[RO,LE]{Automated Verification Applied to Stand-alone Solar Photovoltaic Systems}
\fancyfoot{}
\fancyfoot[LE,RO]{\thepage}
\fancyfoot[CO,CE]{Chapter \thechapter}
\fancyfoot[LO,RE]{A. B. Trindade}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}
\input{chapters/introduction}

\chapter{Background}
\input{chapters/chapter02}

\chapter{Methodology}
\input{chapters/chapter03}

\chapter{Automated Formal Verification of Stand-Alone Solar PV Systems}
\input{chapters/chapter04}

\chapter{Automated Formal Synthesis Optimization Method for Sizing of Stand-Alone Solar PV Systems}
\input{chapters/chapter05}

\chapter{Conclusions}
\fancyfoot[CO,CE]{Conclusions}
\input{chapters/conclusion}

\appendix
\chapter{List of Publications}
\fancyfoot[CO,CE]{Appendix}
\input{chapters/appendix}

\fancyfoot[CO,CE]{References}
%\printbibliography
\renewcommand\bibname{References}
\bibliography{trindadeThesis}{}

>>>>

\documentclass[12pt,twoside]{report}
\usepackage{titlesec}         %para 4 níveis de subsection com numeração
\setcounter{secnumdepth}{4}   %para 4 níveis de subsection com numeração
\setcounter{tocdepth}{4}      %pata 4 níveis no TOC com numeração aparecendo
%\documentclass[12pt,a4paper]{ltxdoc}
%\documentclass[12pt,a4paper]{article}
\usepackage{lmodern}			% Usa a fonte Latin Modern			
\usepackage[T1]{fontenc}		% seleção de códigos de fonte.
\usepackage[utf8]{inputenc}		% determina a codificação utilizada (conversão automática dos acentos)
\usepackage[breaklinks]{hyperref}
\usepackage{parskip}			% espaçamento entre os parágrafos
\usepackage{microtype} 			% para melhorias de justificação
\usepackage{morefloats}			% permite mais floats
\usepackage{setspace}
%\singlespacing
\onehalfspacing
%\doublespacing
%\setstretch{1.1}

%\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{algorithm,algorithmic}
\usepackage{xcolor}
%Alessandro input: makecell package to permite line break inside tables
\usepackage{makecell}
\usepackage[alf]{abntex2cite}	% citacoes

@@

\title{Automated Verification of Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation}
\author{Alessandro Trindade}
\date{31 July 2019}

@@

\input{abstract}
\pagestyle{empty}
%\thispagestyle{empty}
\newpage

@@

\chapter{Introduction}
\pagenumbering{arabic}
\pagestyle{fancy}
\fancyhead{}
\fancyhead[RO,LE]{Automated Verification of Stand-alone Solar Photovoltaic Systems}
\fancyfoot{}
\fancyfoot[LE,RO]{\thepage}
\fancyfoot[CO,CE]{Chapter \thechapter}
\fancyfoot[LO,RE]{A. B. Trindade}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}
\input{chapters/introduction}

\chapter{Background}
\label{chap:background}
\input{chapters/chapter02}

\chapter{Automated Verification and Synthesis Methodologies}
\label{chap:methodology}
\input{chapters/chapter03}

\chapter{Automated Formal Verification of Stand-Alone Solar PV Systems}
\label{chap:automatedverification}
\input{chapters/chapter04}

\chapter{Automated Formal Synthesis Optimization Method for Sizing of Stand-Alone Solar PV Systems}
\label{chap:automatedsynthesis}
\input{chapters/chapter05}

\chapter{Conclusions}
\label{chap:conclusions}
\fancyfoot[CO,CE]{Conclusions}
\input{chapters/conclusion}

\appendix
\chapter{List of Publications}
\label{chap:publications}
\fancyfoot[CO,CE]{Appendix}
\input{chapters/appendix}

\fancyfoot[CO,CE]{References}
%\printbibliography
\renewcommand\bibname{References}
\bibliographystyle{abntex2-num}
\bibliography{trindadeThesis}{}
